On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-03-19 paper/cav_determinisim_main.tex
typos

A summary of main the results are shown in Table~\ref{TableOfExperiments}.  In the column $\max\sigma$ (unrestricted) the value reported is the maximum deviation across all resource utilisation levels, i.e.\ the worst case for a given scenario.  
%
From these results it is clear that scenarios with only pedestrian actors (Tests 5 \& 6) display results within tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. 
%
However, all other scenarios involving vehicles or a mixture of actor types do not meet the required tolerance, with some deviation in actor path as large as $59$cm.
%
\todo[inline,color=green!40]{GC Edit: From these  results it is clear that scenarios with only pedestrian actors (tests 5-6) display results within the permissible tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. However, all other scenarios involving vehicles or a mixture of actor types breach the permissible tolerance that has been set, with some deviation in actor path as large as $59$cm. }
%
Clearly, such a large deviation cannot be acceptable for simulation to be considered a credible verification tool.

@@

A correlation between resource utilisation and simulation variance has been observed in these results which may be due to process scheduling. Rather than liming utilisation of the whole system, another approach may be to promote the scheduling priority of the simulation process which is explored in Section~\ref{r:process_scheduling}. Furthermore, we were keen to investigate the impact of memory access and include a brief investigation of this in Section~\ref{r:numa}. 
%
\todo[inline,color=green!40]{GC Addition: Practitioners may wish to set a stricter resource utilisation level, such as less than 50\% to further reduce the potential dispersion of results if this is required for their chosen application. 
%For this case study a 50\% restriction of resource utilisation would reduce deviation across all experiments to XXX.XXXmm. 
}

>>>>

A summary of the main the results are shown in Table~\ref{TableOfExperiments}.  In the column $\max\sigma$ (unrestricted) the value reported is the maximum deviation across all resource utilisation levels, i.e.\ the worst case for a given scenario.  
%
From these results it is clear that scenarios with only pedestrian actors (Tests 5 \& 6) display results within tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. 
%
However, all other scenarios involving vehicles or a mixture of actor types do not meet the required tolerance, with some deviation in actor path as large as $59$cm.
%
\todo[inline,color=green!40]{GC Edit: From these  results it is clear that scenarios with only pedestrian actors (tests 5-6) display results within the permissible tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. However, all other scenarios involving vehicles or a mixture of actor types breach the permissible tolerance that has been set, with some deviation in actor path as large as $59$cm. }
%
Clearly, such a large deviation cannot be acceptable for simulation to be considered a credible verification tool.

@@

A correlation between resource utilisation and simulation variance has been observed in these results which may be due to process scheduling. Rather than limiting utilisation of the whole system, another approach may be to promote the scheduling priority of the simulation process which is explored in Section~\ref{r:process_scheduling}. Furthermore, we were keen to investigate the impact of memory access and include a brief investigation of this in Section~\ref{r:numa}. 
%
\todo[inline,color=green!40]{GC Addition: Practitioners may wish to set a stricter resource utilisation level, such as less than 50\% to further reduce the potential dispersion of results if this is required for their chosen application. 
%For this case study a 50\% restriction of resource utilisation would reduce deviation across all experiments to XXX.XXXmm. 
}
